
# Load data

```{r eval=FALSE}

# conda activate spatial
library(Seurat)
library(tidyverse)
library(cowplot)
library(Matrix)
library(viridis)
library(presto)
library(harmony)
library(RColorBrewer)
library(patchwork)
library(ggpubr)
library(tictoc)
library(RColorBrewer)
library(Hmisc)
library(corrplot)
library(enrichR)
library(GeneOverlap)
library(WGCNA)
enableWGCNAThreads(nThreads = 8)

set.seed(2021)
colfunc <- colorRampPalette(rev(brewer.pal(11, 'Spectral' )))
theme_set(theme_cowplot())
# scp ../../pipelines/scWGCNA/R/* hpc3:/dfs3b/swaruplab/smorabit/collab/woodlab/cocaine_mouse_2021/Nurr2c_vs_GFP/scWGCNA/bin/
setwd("/dfs3b/swaruplab/smorabit/collab/woodlab/cocaine_mouse_2021/Nurr2c_vs_GFP/scWGCNA")

# source all of the scWGCNA scripts:
scripts <- dir("bin/")
scripts <- scripts[scripts != 'scWGCNA.R']
for(script in scripts){
  source(paste0("bin/", script))
}

# directories
data_dir <- "data/"
fig_dir <- 'figures/'

umap_theme <- theme(
  axis.line=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks=element_blank(),
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  panel.background=element_blank(),
  panel.border=element_blank(),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  plot.background=element_blank(),
  plot.title = element_text(hjust = 0.5)
)

# load seurat obj
seurat_obj <- readRDS('/dfs3b/swaruplab/smorabit/collab/woodlab/cocaine_mouse_2021/Nurr2c_vs_GFP/data/harmony_annotated.rds')

# re-load color scheme:
load('/dfs3b/swaruplab/smorabit/collab/woodlab/cocaine_mouse_2021/Nurr2c_vs_GFP/data/color_scheme.rda')

# directories
data_dir <- "data/"
fig_dir <- 'figures/'

# load mouse <-> human gene name table:
hg38_mm10_genes <- read.table(
  "/dfs3b/swaruplab/smorabit/resources/hg38_mm10_orthologs_2021.txt",
  sep='\t',
  header=TRUE
)
colnames(hg38_mm10_genes) <-c('hg38_id', 'mm10_id', 'mm10_name', 'hg38_name')
hg38_mm10_genes <- dplyr::select(hg38_mm10_genes, c(hg38_name, mm10_name, hg38_id, mm10_id))

# load scWGCNA testing seurat object
cur_seurat <- readRDS(file='data/test_wgcna_seurat.rds')

# # select celltype:
# cur_celltype <- 'MHb-Neuron'
#
# # seurat obj for this celltype
# cur_seurat <- subset(seurat_obj, cell_type == cur_celltype)

```


Running WGCNA

```{r eval=FALSE}

########################################################################
#  Setup Seurat object for scWGCNA
########################################################################

groups <- c('Sample', 'cell_type', 'Group')

cur_seurat <- seurat_obj@meta.data %>% subset(
  cell_type %in% c("LHb-Neuron", "PHb-Neuron", "MHb-Neuron") &
  as.character(Sample) %in% c("Sample-1", "Sample-2")
)
cur_seurat <- seurat_obj[,rownames(cur_seurat)]

# set Idents of Seurat object to cell types
# this is critical because scWGCNA will look at idents to group
Idents(cur_seurat) <- cur_seurat$cell_type

# set up Seurat object
cur_seurat <- SetupForWGCNA(
  cur_seurat, wgcna_name = "MHb",
  gene_select = "fraction",
  fraction = 0.1
)

# construct metacells:
cur_seurat <- MetacellsByGroups(
  seurat_obj = cur_seurat,
  group.by = groups,
  ident.group = 'cell_type'
)

# normalize metacells:
cur_seurat <- NormalizeMetacells(cur_seurat)

########################################################################
#  Construct co-expression networks
########################################################################

# Test different soft powers:
cur_seurat <- TestSoftPowers(cur_seurat, group.by='cell_type', group_name="MHb")

# construct wgcna network:
cur_seurat <- ConstructNetwork(
  cur_seurat, soft_power=8,
  group.by='cell_type', group_name="MHb"
)

# plot the dendrogram
pdf("figures/test_dendro.pdf",height=5, width=8)
PlotDendrogram(cur_seurat, main='Test')
dev.off()

########################################################################
# Compute Module Eigengenes, module connectivity, and module scores
########################################################################

# scale the gene expression matrix in the Seurat object with all
# genes used for WGCNA (might take a while to run):
cur_seurat <- Seurat::ScaleData(
  cur_seurat,
  features = GetWGCNAGenes(cur_seurat),
  vars.to.regress = c('n_genes_by_counts', 'pct_counts_mt')
)

# compute all MEs in the full single-cell dataset
cur_seurat <- ModuleEigengenes(cur_seurat, group.by.vars="Sample")

# compute module connectivity:
cur_seurat <- ModuleConnectivity(cur_seurat)

# change module names:

# compute module expression score & average module expression:
cur_seurat <- ModuleExprScore(cur_seurat, n_genes = 25, method='Seurat')
cur_seurat <- AvgModuleExpr(cur_seurat, n_genes = 100)

########################################################################
# Module correlation analysis
########################################################################

library(igraph)
library(qgraph)

# plot the Module Correlation plot:
pdf("figures/test_ME_correlogram.pdf",height=6, width=6)
ModuleCorrelogram(cur_seurat, sig.level = 0.001, pch.cex=2)
dev.off()

# plot the Module Correlation plot for average exp:
pdf("figures/test_ME_correlogram_avg.pdf",height=6, width=6)
ModuleCorrelogram(cur_seurat, sig.level = 0.001, pch.cex=2, features='average')
dev.off()

# plot the Module Correlation plot for hub scores:
pdf("figures/test_ME_correlogram_scores.pdf",height=6, width=6)
ModuleCorrelogram(cur_seurat, sig.level = 0.001, pch.cex=2, features='scores')
dev.off()

# correlation network
pdf(paste0('figures/test_module_corr_graph.pdf'), width=6, height=6, useDingbats=FALSE)
ModuleCorrNetwork(
  cur_seurat, label_vertices=TRUE, features='scores',
  vertex_size=20, cor_cutoff=.2,
  niter=1000, vertex_frame=TRUE
)
dev.off()

########################################################################
# plot module eigengene & Module genescores featureplots
########################################################################

# plot single ME FeaturePlot
p <- ModuleFeaturePlot(cur_seurat, "blue", features='hMEs', alpha=0.5)
pdf("figures/test_MEFeaturePlot.pdf",height=4, width=4)
p
dev.off()

# plot single ME FeaturePlot shuffle points
# is it actually shuffling??
p1 <- ModuleFeaturePlot(cur_seurat, "blue", features='hMEs', order="shuffle")
p2 <- ModuleFeaturePlot(cur_seurat, "blue", features='hMEs', order=FALSE)
p3 <- ModuleFeaturePlot(cur_seurat, "blue", features='hMEs', order=TRUE)
pdf("figures/test_MEFeaturePlot.pdf",height=4, width=10)
p1 + p2 + p3
dev.off()

# plot all MEs:
plot_list <- ModuleFeaturePlot(cur_seurat)
pdf("figures/test_MEFeaturePlot_multi.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# plot module scores (UCell)
cur_seurat <- ModuleExprScore(cur_seurat, n_genes = 'all', method='UCell')
plot_list <- ModuleFeaturePlot(cur_seurat, features='scores', ucell=TRUE, order=FALSE)
pdf("figures/test_MEFeaturePlot_scores_UCell_multi.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# plot module scores (Seurat)
cur_seurat <- ModuleExprScore(cur_seurat, n_genes = 25, method='Seurat')
plot_list <- ModuleFeaturePlot(cur_seurat, features='scores')
pdf("figures/test_MEFeaturePlot_scores_Seurat_multi.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# plot average module expression
plot_list <- ModuleFeaturePlot(cur_seurat, features='average')
pdf("figures/test_MEFeaturePlot_averages_multi.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

########################################################################
# GO Term enrichment analysis
########################################################################

library(enrichR)
dbs<-c('GO_Biological_Process_2021','GO_Cellular_Component_2021','GO_Molecular_Function_2021','LINCS_L1000_Chem_Pert_up','LINCS_L1000_Chem_Pert_down', 'WikiPathways_2019_Mouse', 'KEGG_2019_Mouse')

# compute GO terms:
cur_seurat <- RunEnrichr(cur_seurat, dbs=dbs)

# make GO term plots:
EnrichrBarPlot(
  cur_seurat,
  outdir = "figures/enrichr_plots",
  n_terms = 10, plot_size = c(5,7),
  logscale=TRUE
)

# enrichr dotplot
p <- EnrichrDotPlot(
  cur_seurat,
  database = dbs[1], n_terms=2
)
pdf(paste0(fig_dir, 'test_GO_dotplot.pdf'), width=10, height=10, useDingbats=FALSE)
p
dev.off()


# add color to enrichdf
modules <- GetModules(cur_seurat)

mod_colors <- select(modules, c(module, color)) %>% distinct
enrich_table$color <- mod_colors[match(enrich_table$module, mod_colors$module), 'color']

########################################################################
# Network plotting:
########################################################################

# individual module networks
ModuleNetworkPlot(cur_seurat)

# hubgene network
pdf(paste0(fig_dir, 'test_hubgene_graph.pdf'), width=7, height=7, useDingbats=FALSE)
HubGeneNetworkPlot(
  cur_seurat,
  n_hubs = 10, n_other=10,
  mods = 'all'
)
dev.off()

########################################################################
# Overlap between modules & marker genes:
########################################################################

library(GeneOverlap)

markers <- read.csv('../DEGs/data/cluster_marker_DEGs.csv')
condition_DEGs <- read.csv('../DEGs/data/cluster_Nurr2c_vs_GFP.csv')

# compute marker gene overlaps
overlap_df <- OverlapModulesDEGs(
  cur_seurat, deg_df = markers,
  fc_cutoff = 2.0
)

# compute condition DEG gene overlaps
overlap_df <- OverlapModulesDEGs(
  cur_seurat, condition_DEGs, fc_cutoff = 0.2
)

# compute condition DEG gene overlaps
overlap_df <- OverlapModulesDEGs(
  cur_seurat, condition_DEGs, fc_cutoff = -0.2
)

# plot odds ratio of the overlap
p <- OverlapDotPlot(overlap_df, plot_var = 'odds_ratio')

pdf(paste0(fig_dir, 'test_overlap_dotplot.pdf'), width=6, height=6, useDingbats=FALSE)
p
dev.off()

# overlap barplot
plot_list <- OverlapBarPlot(
  overlap_df
)

pdf(paste0(fig_dir, 'test_overlap_barplot.pdf'), width=10, height=12, useDingbats=FALSE)
wrap_plots(plot_list, ncol=5)
dev.off()


########################################################################
# save / re-load
########################################################################

saveRDS(cur_seurat, file='data/test_wgcna_seurat.rds')
cur_seurat <- readRDS(file='data/test_wgcna_seurat.rds')

```


Project Modules onto new dataset:

```{r eval=FALSE}

# Seurat object to project to:
seurat_proj <- seurat_obj@meta.data %>% subset(
  cell_type %in% c("LHb-Neuron", "PHb-Neuron", "MHb-Neuron") &
  as.character(Sample) %in% c("Sample-3", "Sample-4")
)
seurat_proj <- seurat_obj[,rownames(seurat_proj)]


# project modules onto new dataset
# if we don't scale it, the result actually looks way different for the MEs!!
seurat_proj <- ProjectModules(
  seurat_obj = seurat_proj,
  seurat_ref = cur_seurat,
  group.by.vars=c("Sample"),
  wgcna_name_proj = "MHb_projected",
  vars.to.regress = c('n_genes_by_counts', 'pct_counts_mt'),
  verbose=TRUE, scale_genes=TRUE
)

# compute module expression score & average module expression:
seurat_proj <- ModuleExprScore(seurat_proj, n_genes = 25, method='Seurat')
seurat_proj <- AvgModuleExpr(seurat_proj, n_genes = 100)

################################################################################
# Plots for projected dataset:
################################################################################

# ME featureplot of projected data:
plot_list <- ModuleFeaturePlot(seurat_proj, features='hMEs', order='shuffle')
pdf("figures/test_MEFeaturePlot_projected.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# ME featureplot of projected data:
plot_list <- ModuleFeaturePlot(seurat_proj, features='scores', order='shuffle')
pdf("figures/test_MEFeaturePlot_projected_scores.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# ME correlogram of projected data:
pdf("figures/test_ME_correlogram_projected.pdf",height=6, width=6)
ModuleCorrelogram(seurat_proj, sig.level = 0.001, pch.cex=2, features='hMEs')
dev.off()

# ME correlogram of projected data:
pdf("figures/test_ME_correlogram_score_vs_MEs.pdf",height=6, width=6)
ModuleCorrelogram(
  cur_seurat, MEs2 = GetModuleScores(cur_seurat),
  sig.level = 0.001, pch.cex=2, features='hMEs'
)
dev.off()


```

ROC Curve comparing original modules & projected modules in a shared cell space

```{r eval=FALSE}

group.by <- 'annotation'
groups <- as.character(unique(cur_seurat@meta.data[[group.by]]))

# get Modules
modules <- GetModules(cur_seurat)
mods <- levels(modules$module)
mods <- mods[mods != 'grey']

# get MEs:
MEs <- GetMEs(cur_seurat, harmonized=TRUE) %>% mutate(group = cur_seurat@meta.data[[group.by]])
MEs_p <- as.data.frame(GetMEs(seurat_proj, harmonized=TRUE)) %>% mutate(group = seurat_proj@meta.data[[group.by]])

# compute average MEs in each group:
avg_MEs <- MEs %>% group_by(group) %>% summarise(across(!!mods, mean))
avg_MEs_p <- MEs_p %>% group_by(group) %>% summarise(across(!!mods, mean))
groups <- avg_MEs$group

# scale each column between 0 & 1
avg_MEs <- avg_MEs %>% summarise(across(!!mods, scale01))
avg_MEs_p <- avg_MEs_p %>% summarise(across(!!mods, scale01))

# convert to binary labels:
thresh <- 0.75
labels <- avg_MEs %>% purrr::map(~ifelse(. >= thresh, TRUE, FALSE))
labels <- as.data.frame(do.call(cbind, labels));
rownames(labels) <- as.character(groups)

predictions <- avg_MEs_p %>% purrr::map(~ifelse(. >= thresh, TRUE, FALSE))
predictions <- as.data.frame(do.call(cbind, predictions));
rownames(predictions) <- as.character(groups)

# loop over modules to compute ROC curves:
plot_df <- data.frame()
conf_df <- data.frame()
auc_list <- list()
mod_colors <- list()
for(cur_mod in mods){
  print(cur_mod)
  cur_color <- modules %>% subset(module == cur_mod) %>% .$color %>% unique
  mod_colors[[cur_mod]] <- cur_color

  # compute ROC
  rocobj <- pROC::roc(labels[,cur_mod], avg_MEs_p[[cur_mod]])
  auc_list[[cur_mod]] <- as.numeric(rocobj$auc)
  # confidence intervals:
  # sens_ci <- ci.se(rocobj)

  cur_df <- data.frame(
    specificity = 1-rocobj$specificities,
    sensitivity = rocobj$sensitivities,
    #auc = rocobj$auc,
    module = cur_mod,
    color = cur_color,
    auc = as.numeric(rocobj$auc)
  #  ci_lo = sens_ci[,1],
  #  ci_med = sens_ci[,2],
  #  ci_hi = sens_ci[,3]

  )
  plot_df <- rbind(plot_df, cur_df)

  cur_conf <- as.data.frame(ci.se(rocobj))
  cur_conf$sensitivity <- 1-as.numeric(rownames(cur_conf))
  cur_conf$module <- cur_mod
  cur_conf$color <- cur_color
  conf_df <- rbind(conf_df, cur_conf)

}
colnames(conf_df)[1:3] <- c('lo', 'mid', 'hi')



library(pROC)
rocobj <- pROC::roc(labels$red, avg_MEs_p$red)
rocobj$auc

sens_ci <- ci.se(rocobj)


p <- ggroc(rocobj)

pdf(paste0(fig_dir, 'test_ROC_blue.pdf'), width=6, height=6)
p
dev.off()
#
#
# # confidence intervals:
# sens_ci <- ci.se(rocobj)
#
#
# plot_df <- data.frame(
#   specificity = rocobj$specificities,
#   sensitivity = 1-rocobj$sensitivities,
#   #auc = rocobj$auc,
#   module = "blue",
#   color = "blue"
# #  ci_lo = sens_ci[,1],
# #  ci_med = sens_ci[,2],
# #  ci_hi = sens_ci[,3]
#
# )

plot_df <- plot_df %>% group_by(module) %>% arrange(sensitivity)
conf_df <- conf_df %>% group_by(module) %>% arrange(sensitivity)
auc_df <- distinct(plot_df[,c('module', 'auc')])

p <- plot_df %>% ggplot(
  aes(x=specificity, y=sensitivity, color=module, fill=module),
) +
  geom_line() +
  geom_ribbon(
    data=conf_df,
    aes(x = sensitivity, ymin=lo, ymax=hi, fill=module),
    inherit.aes=FALSE, alpha=0.4
  ) +
  scale_color_manual(values = unlist(mod_colors)) +
  scale_fill_manual(values = unlist(mod_colors)) +
  scale_x_continuous(breaks = c(0, 0.5, 1), labels=c("0", "0.5", "1")) +
  scale_y_continuous(breaks = c(0, 0.5, 1), labels=c("0", "0.5", "1")) +
  xlab("1 - Specificity (FPR)") + ylab("Sensitivity (TPR)") +
  geom_text(
    data = auc_df,
    aes(color=module),
    x=0.75, y=0.1, label=paste0("AUC: ", format(auc_df$auc, digits=2)),
    inherit.aes=FALSE, size=4, color='black'
  )
  #annotate("text", x=0.75, y=0.1, label=paste0("AUC: ", plot_df$auc))
  # theme(
  #   axis.text = element_blank(),
  #   axis.ticks = element_blank()
  # )



pdf(paste0(fig_dir, 'test_ROC.pdf'), width=9, height=6)
p + facet_wrap(~module, ncol=5) + NoLegend()
dev.off()


unlist(auc_list)

```


Project onto human AD dataset:

```{r eval=FALSE}

# load AD NatGen dataset
NucSeq <- readRDS('/dfs3b/swaruplab/smorabit/analysis/AD_NucSeq_2019/batch_correction/liger/update/celltype-analysis/data/NucSeq_batch_correct_seurat.rds')

# keep only a few samples:
NucSeq <- subset(NucSeq, Sample.ID %in% c("Sample-100", "Sample-45"))

NucSeq <- ProjectModules(
  seurat_obj=NucSeq,
  seurat_ref=cur_seurat,
  gene_mapping=hg38_mm10_genes,
  genome1_col="mm10_name",
  genome2_col="hg38_name",
  scale_genes=TRUE,
  wgcna_name_proj="MHb_projected"
)

# compute module expression score & average module expression:
NucSeq <- ModuleExprScore(NucSeq, n_genes = 25, method='Seurat')

# ME featureplot of projected data:
plot_list <- ModuleFeaturePlot(NucSeq, features='scores', order='shuffle', reduction='umap')
pdf("figures/test_MEFeaturePlot_projected_human.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()


# ME correlogram of projected data:
pdf("figures/test_ME_correlogram_projected_human.pdf",height=6, width=6)
ModuleCorrelogram(subset(NucSeq, Cell.Type == 'ASC'), sig.level = 0.001, pch.cex=2, features='hMEs')
dev.off()

```



Test changing the module names

```{r eval=FALSE}

# cur_seurat_backup <- cur_seurat
cur_seurat <- cur_seurat_backup

# run RenameModules
cur_seurat <- ResetModuleNames(
  cur_seurat,
  new_name = "MHb"
)

plot_list <- ModuleFeaturePlot(
  cur_seurat,
  features='hMEs',
  order=TRUE
)

pdf("figures/test_MEFeaturePlot_renamed.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# plot the Module Correlation plot:
pdf("figures/test_ME_correlogram_renamesd.pdf",height=6, width=6)
ModuleCorrelogram(cur_seurat, sig.level = 0.001, pch.cex=2)
dev.off()


```

Test changing colors

```{r eval=FALSE}

library(MetBrewer)

# new_colors <- paste0(met.brewer("Morgenstern", n=length(mod_colors)-1))
# cur_seurat <- cur_seurat_backup

modules <- GetModules(cur_seurat)
mods <- levels(modules$module)
mod_colors <- select(modules, c(module, color)) %>%
  distinct %>% arrange(module) %>% .$color
n_colors <- length(mod_colors) -1

new_colors <- paste0(met.brewer("Tiepolo", n=n_colors))
cur_seurat <- ResetModuleColors(cur_seurat, new_colors)

plot_list <- ModuleFeaturePlot(
  cur_seurat,
  features='scores',
  # restrict_range=FALSE,
  ucell=TRUE,
  order=FALSE
)

pdf("figures/test_MEFeaturePlot_recolored.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

```

TF overlap with genes using motif matchr

```{r eval=FALSE}

library(motifmatchr)
library(TFBSTools)
library(BSgenome.Mmusculus.UCSC.mm10)
library(JASPAR2018)
library(JASPAR2020)
library(EnsDb.Mmusculus.v79)
library(GenomicRanges)
library(ggpubr)
library(ggrepel)
library(cowplot)
theme_set(theme_cowplot())

pfm_core <- TFBSTools::getMatrixSet(
  x = JASPAR2020,
  opts = list(collection = "CORE", tax_group = 'vertebrates', all_versions = FALSE)
)

# get a dataframe of just the motif name and the motif ID:
motif_df <- data.frame(
  motif_name = purrr::map(1:length(pfm_core), function(i){pfm_core[[i]]@name}) %>% unlist,
  motif_ID = purrr::map(1:length(pfm_core), function(i){pfm_core[[i]]@ID}) %>% unlist
)

# get promoter regions for this species (mouse for now)
# THIS DOES NOT WORK IF I USE X & Y

gene.promoters <- promoters(EnsDb.Mmusculus.v79, filter = ~ gene_biotype == "protein_coding") %>% subset(seqnames %in% c(1:19))

gene.coords <- genes(EnsDb.Mmusculus.v79, filter = ~ gene_biotype == "protein_coding") %>% subset(seqnames %in% c(1:19))

gene.promoters$symbol <- gene.coords$symbol[match(gene.promoters$gene_id, names(gene.coords))]
gene.promoters <- keepSeqlevels(gene.promoters, value= levels(droplevels(seqnames(gene.promoters))))

# rename seqlevels
old_levels <- levels(seqnames(gene.promoters))
new_levels <- ifelse(old_levels %in% c('X', 'Y'), old_levels, paste0('chr', old_levels))
gene.promoters <- renameSeqlevels(gene.promoters, new_levels)


# GenomeInfoDb::seqlevelsStyle(gene.promoters) <- 'UCSC'
genome(seqinfo(gene.promoters)) <- 'mm10'

# set up promoters object
my_promoters <- GRanges(
  seqnames =  droplevels(seqnames(gene.promoters)),
  IRanges(
    start = start(gene.promoters),
    end = end(gene.promoters)
  ),
  symbol = gene.promoters$symbol,
  genome='mm10'
)

# match the motifs with the promoters
motif_ix <- matchMotifs(pfm_core, my_promoters, genome='mm10');

x <- motifMatches(motif_ix)
rownames(x) <- my_promoters$symbol

# cur_gene for genes in Seurat object,
#   get motif matches for this gene.
#   update ongoing list
#   some genes have multiple promoter regions so maybe just check for any
#   binding site in any column?



# Make a set of peaks
data(example_motifs, package = "motifmatchr")

peaks <- GRanges(seqnames = c("chr1","chr2","chr2"),
                 ranges = IRanges(start = c(76585873,42772928,100183786),
                                  width = 500))
motif_ix <- matchMotifs(example_motifs[1:2], peaks, genome = "mm10")

motif_ix <- matchMotifs(pfm_core, peaks, genome = "mm10")

```


Project onto a mouse visium dataset (one of our new ones?)

```{r eval=FALSE}



```



Module Eigengene Violin Plots

```{r eval=FALSE}

MEs <- GetMEs(cur_seurat)
plot_df <- cbind(cur_seurat@meta.data, MEs)
mods <- colnames(MEs)

plot_list <- list()
for(cur_mod in mods){

  plot_list[[cur_mod]] <- ggplot(plot_df, aes_string(x="annotation", y=cur_mod, fill="annotation")) +
    geom_violin() +
    geom_boxplot(outlier.shape=NA, width=.2, fill='white') +
    geom_hline(yintercept=0, linetype='dashed') +
    NoLegend() + RotatedAxis() +
    xlab('') + theme(
      axis.ticks.x=element_blank(),
      axis.text.x=element_blank(),
      plot.margin = margin(t = 0,  # Top margin
                             r = 0,  # Right margin
                             b = 0,  # Bottom margin
                             l = 0)
    )
}

pdf("figures/test_ME_violin.pdf",height=10, width=10)
wrap_plots(plot_list, ncol=1)
dev.off()


```





















Testing scWGCNA functions

```{r eval=FALSE}


################################################################################
# testing ConstructMetacells
################################################################################

cur_seurat <- subset(seurat_obj, cell_type == cur_celltype & Sample == 'Sample-1')

meta_list <- list(
  "Sample" = "Sample-1",
  "Group" = 'Nurr2c',
  "cell_type" = cur_celltype
)

cur_seurat <- ConstructMetacells(
  cur_seurat, name="MHb",
  k=50, reduction='umap',
  assay='RNA', slot='counts',
  meta = meta_list
)
cur_seurat@misc

# pass invalid reduction
cur_seurat <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='BAD',
  assay='RNA', slot='counts',
  meta = meta_list
)

# pass invalid assay
cur_seurat <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='umap',
  assay='BAD', slot='counts',
  meta = meta_list
)


################################################################################
# testing NormalizeMetacells
################################################################################

cur_seurat <- subset(seurat_obj, cell_type == cur_celltype & Sample == 'Sample-1')

meta_list <- list(
  "Sample" = "Sample-1",
  "Group" = 'Nurr2c',
  "cell_type" = cur_celltype
)

cur_seurat <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='umap',
  assay='RNA', slot='counts',
  meta = meta_list
)

# run with default settings
NormalizeMetacells(cur_seurat)

# pass additional settings to NormalizeData
NormalizeMetacells(cur_seurat, scale.factor=100
NormalizeMetacells(cur_seurat, scale.factor=100, verbose=FALSE)

################################################################################
# testing ScaleMetacells
################################################################################

cur_seurat <- subset(seurat_obj, cell_type == cur_celltype & Sample == 'Sample-1')
cur_seurat

meta_list <- list(
  "Sample" = "Sample-1",
  "Group" = 'Nurr2c',
  "cell_type" = cur_celltype
)

cur_seurat <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='umap',
  assay='RNA', slot='counts',
  meta = meta_list
)
dim(cur_seurat)

# run with default settings
cur_seurat <- NormalizeMetacells(cur_seurat)
dim(cur_seurat)

# default settings
ScaleMetacells(cur_seurat)

# use ScaleData settings
ScaleMetacells(cur_seurat, scale.max=5)
ScaleMetacells(cur_seurat, features=rownames(cur_seurat)[1:1000])


################################################################################
# testing RunPCAMetacells, RunHarmonyMetacells, RunUMAPMetacells
################################################################################

cur_seurat <- subset(seurat_obj, cell_type == cur_celltype & Sample == 'Sample-1')

meta_list <- list(
  "Sample" = "Sample-1",
  "Group" = 'Nurr2c',
  "cell_type" = cur_celltype
)

cur_seurat <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='umap',
  assay='RNA', slot='counts',
  meta = meta_list
)

# run with default settings
cur_seurat <- NormalizeMetacells(cur_seurat)
cur_seurat <- ScaleMetacells(cur_seurat)
cur_seurat <- RunPCAMetacells(cur_seurat, features=VariableFeatures(cur_seurat))
cur_seurat <- RunHarmonyMetacells(
  cur_seurat,
  group.by='Sample',
  dims=1:15,
  max.iter.harmony=3
)
cur_seurat <- RunUMAPMetacells(cur_seurat, reduction='harmony', dims=1:15)

p1 <- DimPlotMetacells(cur_seurat, group.by='cell_type') + umap_theme
p2 <- DimPlotMetacells(cur_seurat, group.by='Sample') + umap_theme

pdf('figures/test_metacell_umap.pdf', width=10, height=4)
p1 | p2
dev.off()

################################################################################
# construct metacells for each metacell group and merge into one seurat obj
################################################################################

library(future.apply)
plan(sequential)
# check how many cores:
# availableCores()
# plan(multicore, workers=8)
# options(future.globals.maxSize= 16*1024^3 )


groups <- c('Sample', 'cell_type', 'Group')


# make a seurat obj for testing:
test_seurat <- seurat_obj@meta.data %>% subset(
  cell_type %in% c("LHb-Neuron", "PHb-Neuron", "MHb-Neuron"),
  as.character(Sample) %in% c("Sample-1", "Sample-2")
)
test_seurat <- seurat_obj[,rownames(test_seurat)]



# test using multiple meta-data columns for grouping
out <- MetacellsByGroups(
  seurat_obj = test_seurat,
  group.by = groups
)

# test using only one meta-data column for grouping
out <- MetacellsByGroups(
  seurat_obj = test_seurat,
  group.by = c("Sample")
)


################################################################################
# Use UMAP versus harmony for metacell construction?
################################################################################

#cur_seurat <- cur_seurat[genes.keep,]
cur_seurat <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='umap',
  assay='RNA', slot='counts',
  meta = meta_list
)
cur_seurat@misc$wgcna_metacell_obj <- NormalizeData(cur_seurat@misc$wgcna_metacell_obj)



cur_seurat2 <- ConstructMetacells(
  cur_seurat, name="test",
  k=50, reduction='harmony',
  assay='RNA', slot='counts'
)
cur_seurat2@misc$wgcna_metacell_obj <- NormalizeData(cur_seurat2@misc$wgcna_metacell_obj)


# correlate metacells?

# average expression in 1
expr_mat1 <- Seurat::GetAssayData(
  cur_seurat@misc$wgcna_metacell_obj,
  slot = 'data'
)
avg_exp1 <- rowMeans(expr_mat1)

expr_mat2 <- Seurat::GetAssayData(
  cur_seurat2@misc$wgcna_metacell_obj,
  slot = 'data'
)
avg_exp2 <- rowMeans(expr_mat2)

exp_cor <- stats::cor(
  x = as.numeric(avg_exp1),
  y = as.numeric(avg_exp2), method='pearson'
)
exp_cor

df <- data.frame(
  'umap' = avg_exp1,
  'harmony' = avg_exp2
)

p <- ggplot(df, aes(x=umap, y=harmony)) +
  geom_point() +
  geom_smooth(method = 'lm', color='black') +
  stat_cor(p.accuracy = 0.00001, r.accuracy = 0.000001, color='black', label.y = 0.9, label.x=0) +
  xlab('Average Expression, UMAP aggregation') + ylab('Average Expression, Harmony aggregation')


pdf('figures/umap_harmony_metacell_correlation.pdf', width=5, height=5)
p
dev.off()



################################################################################
# testing SelectNetworkGenes
################################################################################

# default settings
cur_seurat <- SelectNetworkGenes(cur_seurat)
length(cur_seurat@misc$wgcna_genes)

# custom gene list with good genes
test_genes <- c(head(VariableFeatures(cur_seurat), 600))
cur_seurat <- SelectNetworkGenes(cur_seurat, type='custom', gene_list = test_genes)

# custom gene list with few genes
test_genes <- c(head(VariableFeatures(cur_seurat), 60))
cur_seurat <- SelectNetworkGenes(cur_seurat, type='custom', gene_list = test_genes)

# custom gene list with bad genes
test_genes <- c(VariableFeatures(cur_seurat), 'APOE', 'BADGENE')
cur_seurat <- SelectNetworkGenes(cur_seurat, type='custom', gene_list = test_genes)

# fraction with default:
cur_seurat <- SelectNetworkGenes(cur_seurat, type='fraction')
length(cur_seurat@misc$wgcna_genes)

# fraction with 10%:
cur_seurat <- SelectNetworkGenes(cur_seurat, type='fraction', fraction = 0.10)
length(cur_seurat@misc$wgcna_genes)

# fraction with 100% (should throw an error)
cur_seurat <- SelectNetworkGenes(cur_seurat, type='fraction', fraction = 1.0)
length(cur_seurat@misc$wgcna_genes)

# all genes
cur_seurat <- SelectNetworkGenes(cur_seurat, type='all')

# invalid selection type
cur_seurat <- SelectNetworkGenes(cur_seurat, type='random')

# head the wgcna_genes
head(seurat_obj@misc$wgcna_genes)

```




















Test module eigengenes function

```{r eval=FALSE}

# compute one ME
cur_seurat <- ComputeModuleEigengene(cur_seurat, group.by.vars=NULL, cur_mod="yellow")

# compute one ME and harmonize
cur_seurat <- ComputeModuleEigengene(cur_seurat, group.by.vars="Sample", cur_mod="yellow")

# compute one ME and pass extra variables to RunPCA:
cur_seurat <- ComputeModuleEigengene(cur_seurat, group.by.vars="Sample", cur_mod="yellow", npcs=30)

# compute one ME and pass extra variables to RunPCA and to RunHarmony:
cur_seurat <- ComputeModuleEigengene(cur_seurat, group.by.vars="Sample", cur_mod="yellow", npcs=30, dims.use=1:30)

# compute all MEs
cur_seurat <- ModuleEigengenes(cur_seurat, group.by.vars="Sample", npcs=30, dims.use=1:30)

saveRDS(cur_seurat, file='data/test_wgcna_seurat.rds')





Make my own module eigengenes function
```{r eval=FALSE}

# loop over modules:
me_list <- list()
harmonized_me_list <- list()
modules <- unique(cur_seurat@misc$wgcna_net$colors)

for(cur_mod in modules){

  print(cur_mod)
  cur_genes <- names(cur_seurat@misc$wgcna_net$colors[cur_seurat@misc$wgcna_net$colors == cur_mod])

  cur_seurat <- RunPCA(cur_seurat, features =cur_genes, reduction.key=paste0('PCA', cur_mod), verbose=FALSE)

  cur_seurat <- RunHarmony(cur_seurat, group.by.vars="Sample", reduction='pca')

  cur_harmonized_me <- cur_seurat@reductions$harmony@cell.embeddings[,1]
  harmonized_me_list[[cur_mod]] <- cur_harmonized_me

  cur_me <- cur_seurat@reductions$pca@cell.embeddings[,1]
  me_list[[cur_mod]] <- cur_me

}

test <- RunPCA(cur_seurat, features =cur_genes, reduction.key=paste0('PCA', cur_mod), verbose=FALSE)@reductions$pca@cell.embeddings

cur_seurat@reductions$ME <- Seurat::CreateDimReducObject(
  embeddings = test,
  assay = Seurat::DefaultAssay(cur_seurat)
)


test <- do.call(cbind, me_list)
colnames(test) <- paste0('ME_', colnames(test))
modules <- colnames(test)
modules <- modules[modules != 'ME_grey']

plot_df <- cbind(cur_seurat@meta.data, test)

plot_list <- list()
for(cur_mod in modules){

  # get color from mod:
  cur_color <- str_split(cur_mod, '_')[[1]][2]

  print(cur_mod)
  plot_range <- plot_df[[cur_mod]] %>% range
  if(abs(plot_range[1]) > abs(plot_range[2])){
    plot_range[1] <- -1*plot_range[2]
  } else{
    plot_range[2] <- -1*plot_range[1]
  }

  plot_df[[cur_mod]] <- ifelse(plot_df[[cur_mod]] > plot_range[2], plot_range[2], plot_df[[cur_mod]])
  plot_df[[cur_mod]] <- ifelse(plot_df[[cur_mod]] < plot_range[1], plot_range[1], plot_df[[cur_mod]])

  plot_list[[cur_mod]] <- plot_df %>%
    arrange_(cur_mod) %>%
    ggplot(aes_string(x="UMAP_1", y="UMAP_2", color=cur_mod)) +
    geom_point(size=0.5) +
    scale_color_gradient2(low='grey75', mid='grey95', high=cur_color) +
    umap_theme + ggtitle('')

}

pdf('figures/test_me_featureplot.pdf', width=10, height=10)
wrap_plots(plot_list, ncol=2)
dev.off()




plot_df %>% arrange_(cur_mod) %>% head

plot_df %>% arrange(UQ(cur_mod)) %>% head


p1 <- plot_df %>%
  ggplot(aes(x=UMAP_1, y=UMAP_2, color=ME_blue)) +
  geom_point(size=0.5) +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red')) +
  umap_theme + ggtitle(cur_mod)



p2 <- plot_df %>%
  ggplot(aes(x=UMAP_1, y=UMAP_2, color=ME_turquoise)) +
  geom_point(size=0.5) +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red')) +
  umap_theme + ggtitle(cur_mod)

p3 <- plot_df %>%
  ggplot(aes(x=UMAP_1, y=UMAP_2, color=ME_yellow)) +
  geom_point(size=0.5) +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red')) +
  umap_theme + ggtitle(cur_mod)



p4 <- plot_df %>%
  ggplot(aes(x=UMAP_1, y=UMAP_2, color=ME_brown)) +
  geom_point(size=0.5) +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red')) +
  umap_theme + ggtitle(cur_mod)


p5 <- plot_df %>%
  ggplot(aes(x=UMAP_1, y=UMAP_2, color=ME_grey)) +
  geom_point(size=0.5) +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red')) +
  umap_theme + ggtitle(cur_mod)

pdf('figures/test_me_featureplot.pdf', width=12,height=9)
(p1 + p2 + p3 ) / (p4 + p5)
dev.off()







cur_mod <- 'blue'
cur_genes <- names(cur_seurat@misc$wgcna_net$colors[cur_seurat@misc$wgcna_net$colors == cur_mod])

test <- RunPCA(cur_seurat, features =cur_genes, reduction.key=paste0('PCA', cur_mod))

test <- RunHarmony(test, group.by.vars="Sample", reduction='pca')



# plot harmonized ME

cur_me <- test@reductions$harmony@cell.embeddings[,1]
test@meta.data$test_me <- cur_me

plot_range <- test$test_me %>% range
if(abs(plot_range[1]) > abs(plot_range[2])){
  plot_range[1] <- -1*plot_range[2]
} else{
  plot_range[2] <- -1*plot_range[1]
}
plot_range

test$test_me <- ifelse(test$test_me > plot_range[2], plot_range[2], test$test_me)
test$test_me <- ifelse(test$test_me < plot_range[1], plot_range[1], test$test_me)

p1 <- FeaturePlot(test, features='test_me', order=TRUE) + umap_theme +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red'), limits=plot_range) +
  ggtitle('Harmonized ME')

# plot ME

cur_me <- test@reductions$pca@cell.embeddings[,1]
test@meta.data$test_me <- cur_me

plot_range <- test$test_me %>% range
if(abs(plot_range[1]) > abs(plot_range[2])){
  plot_range[1] <- -1*plot_range[2]
} else{
  plot_range[2] <- -1*plot_range[1]
}
plot_range

test$test_me <- ifelse(test$test_me > plot_range[2], plot_range[2], test$test_me)
test$test_me <- ifelse(test$test_me < plot_range[1], plot_range[1], test$test_me)

p2 <- FeaturePlot(test, features='test_me', order=TRUE) + umap_theme +
  scale_color_gradient2(low=scales::muted('blue'), mid='lightgrey', high=scales::muted('red'), limits=plot_range) +
  ggtitle('ME')

pdf('figures/test_me_featureplot.pdf', width=10,height=5)
p1 | p2
dev.off()


```
