
# Load data

```{r eval=FALSE}

# conda activate spatial
library(Seurat)
library(tidyverse)
library(cowplot)
library(Matrix)
library(viridis)
library(presto)
library(harmony)
library(RColorBrewer)
library(patchwork)
library(ggpubr)
library(tictoc)
library(RColorBrewer)
library(Hmisc)
library(corrplot)
library(enrichR)
library(GeneOverlap)
library(WGCNA)
enableWGCNAThreads(nThreads = 8)

set.seed(2021)
colfunc <- colorRampPalette(rev(brewer.pal(11, 'Spectral' )))
theme_set(theme_cowplot())
# scp ../../pipelines/scWGCNA/R/* hpc3:/dfs3b/swaruplab/smorabit/analysis/scWGCNA/bin/
setwd("/dfs3b/swaruplab/smorabit/collab/woodlab/cocaine_mouse_2021/Nurr2c_vs_GFP/scWGCNA")

# source all of the scWGCNA scripts:
scripts <- dir("bin/")
scripts <- scripts[scripts != 'scWGCNA.R']
for(script in scripts){
  source(paste0("bin/", script))
}

# directories
data_dir <- "data/"
fig_dir <- 'figures/'

umap_theme <- theme(
  axis.line=element_blank(),
  axis.text.x=element_blank(),
  axis.text.y=element_blank(),
  axis.ticks=element_blank(),
  axis.title.x=element_blank(),
  axis.title.y=element_blank(),
  panel.background=element_blank(),
  panel.border=element_blank(),
  panel.grid.major=element_blank(),
  panel.grid.minor=element_blank(),
  plot.background=element_blank(),
  plot.title = element_text(hjust = 0.5)
)

# load seurat obj from AD NatGen paper:
NucSeq <- readRDS('/dfs3b/swaruplab/smorabit/analysis/AD_NucSeq_2019/batch_correction/liger/update/celltype-analysis/data/NucSeq_batch_correct_seurat.rds')

# load NatGen color scheme:
load('/dfs3b/swaruplab/smorabit/analysis/AD_NucSeq_2019/batch_correction/liger/update/celltype-analysis/data/color_scheme.rda')


# directories
data_dir <- "data/"
fig_dir <- 'figures/'

# load mouse <-> human gene name table:
hg38_mm10_genes <- read.table(
  "/dfs3b/swaruplab/smorabit/resources/hg38_mm10_orthologs_2021.txt",
  sep='\t',
  header=TRUE
)
colnames(hg38_mm10_genes) <-c('hg38_id', 'mm10_id', 'mm10_name', 'hg38_name')
hg38_mm10_genes <- dplyr::select(hg38_mm10_genes, c(hg38_name, mm10_name, hg38_id, mm10_id))

# load scWGCNA testing seurat object
seurat_obj <- readRDS(file='data/test_wgcna_seurat.rds')

# # select celltype:
# cur_celltype <- 'MHb-Neuron'
#
# # seurat obj for this celltype
# seurat_obj <- subset(seurat_obj, cell_type == cur_celltype)

```

Human
Run scWGCNA on 80/20 train/test split
project Modules onto test data
run ROC code

```{r eval=FALSE}

################################################################################
# Setup data
#
# Note: all genes have already been Scaled for this Seurat object
################################################################################

set.seed(12345)

# get only control samples
seurat_obj <- subset(NucSeq, Diagnosis == 'Control' & Cell.Type != "PER.END")
table(seurat_obj$Cell.Type, seurat_obj$Sample.ID)

# 80/20 train/test split:
train_prop = 0.8
train_cells <- sample(colnames(seurat_obj), round(train_prop * ncol(seurat_obj)))
seurat_obj$wgcna_train <- ifelse(colnames(seurat_obj) %in% train_cells, 'train', 'test')

# setup training data for scWGCNA:
seurat_obj <- SetupForWGCNA(
  seurat_obj, wgcna_name = "train",
  gene_select  = "fraction",
  fraction = 0.1
)

# construct metacells:
seurat_obj <- MetacellsByGroups(
  seurat_obj = seurat_obj,
  group.by = c("Cell.Type", "Sample.ID"),
  cells.use = rownames(subset(seurat_obj@meta.data, wgcna_train == 'train')),
  k = 25,
  ident.group = 'Cell.Type'
)

# normalize metacells:
seurat_obj <- NormalizeMetacells(seurat_obj)

########################################################################
#  Construct co-expression networks
########################################################################

# Test different soft powers:
seurat_obj <- TestSoftPowers(seurat_obj, group.by='Cell.Type', group_name="ASC")

# construct wgcna network:
seurat_obj <- ConstructNetwork(
  seurat_obj, soft_power=8,
  group.by='Cell.Type', group_name="ASC"
)

# plot the dendrogram
pdf("figures/test_human_ASC_dendro.pdf",height=5, width=8)
PlotDendrogram(seurat_obj, main='ASC')
dev.off()


########################################################################
# Compute Module Eigengenes, module connectivity, and module scores
########################################################################

# compute all MEs in the full single-cell dataset
seurat_obj <- ModuleEigengenes(seurat_obj, group.by.vars="Batch")

# compute module connectivity:
seurat_obj <- ModuleConnectivity(seurat_obj)

# compute module hub gene scores:
seurat_obj <- ModuleExprScore(seurat_obj, n_genes = 25, method='Seurat')
seurat_obj <- AvgModuleExpr(seurat_obj, n_genes = 100)

# run RenameModules
seurat_obj <- ResetModuleNames(
  seurat_obj,
  new_name = "ASC-M"
)
print(names(GetModules(seurat_obj)))

# reset colors:
library(MetBrewer)
modules <- GetModules(seurat_obj)
mods <- levels(modules$module)
mod_colors <- select(modules, c(module, color)) %>%
  distinct %>% arrange(module) %>% .$color
n_colors <- length(mod_colors) -1

new_colors <- paste0(met.brewer("Tiepolo", n=n_colors))
seurat_obj <- ResetModuleColors(seurat_obj, new_colors)

plot_list <- ModuleFeaturePlot(seurat_obj, order='shuffle')
pdf("figures/test_MEFeaturePlot_human_hMEs.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# plot module scores (Seurat)
plot_list <- ModuleFeaturePlot(seurat_obj, features='scores')
pdf("figures/test_MEFeaturePlot_human_scores.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()

# save processed object:
saveRDS(seurat_obj, file=paste0(data_dir, 'human_AD_NatGen_scWGCNA.rds'))
seurat_obj <- readRDS(file=paste0(data_dir, 'human_AD_NatGen_scWGCNA.rds'))

```

Make ROC functions

should be able to take one seurat object with a train/test metadata column,
or to take two seurat objects as input


```{r eval=FALSE}

library(pROC)

# get Modules
modules <- GetModules(seurat_obj)
mods <- levels(modules$module)
mods <- mods[mods != 'grey']

seurat_obj$wgcna_train_binary <- ifelse(seurat_obj$wgcna_train == 'train', TRUE, FALSE)

# ROC with a single seurat obj
seurat_obj <- ComputeROC(
  seurat_obj,
  group.by = 'monocle_clusters_umap_ID',
  split_col = 'wgcna_train_binary',
  features = 'hMEs',
  harmony_group_vars = "Batch",
  scale_genes = FALSE,
  verbose=TRUE,
  return_seurat=TRUE
)

roc_data <- GetROCData(seurat_obj)
head(roc_data$roc)

# plot the ROC Curves
p <- ROCCurves(seurat_obj=seurat_obj)
pdf(paste0(fig_dir, 'test_ROC_human_func.pdf'), width=8, height=6)
p + facet_wrap(~module, ncol=4) + NoLegend()
dev.off()

```

Analysis for Fig 1 of the scWGCNA paper:

1. Integrate Zhou et al AD dataset & Morabito/Miyoshi et al AD dataset
2. Train/Test scWGCNA on Zhou with 80/20 split, use Morabito et al as validation set

```{r eval=FALSE}

# TODO


```


Project onto human AD dataset:

```{r eval=FALSE}

# load AD NatGen dataset
NucSeq <- readRDS('/dfs3b/swaruplab/smorabit/analysis/AD_NucSeq_2019/batch_correction/liger/update/celltype-analysis/data/NucSeq_batch_correct_seurat.rds')

# keep only a few samples:
NucSeq <- subset(NucSeq, Sample.ID %in% c("Sample-100", "Sample-45"))

NucSeq <- ProjectModules(
  seurat_obj=NucSeq,
  seurat_ref=seurat_obj,
  gene_mapping=hg38_mm10_genes,
  genome1_col="mm10_name",
  genome2_col="hg38_name",
  scale_genes=TRUE,
  wgcna_name_proj="MHb_projected"
)

# compute module expression score & average module expression:
NucSeq <- ModuleExprScore(NucSeq, n_genes = 25, method='Seurat')

# ME featureplot of projected data:
plot_list <- ModuleFeaturePlot(NucSeq, features='scores', order='shuffle', reduction='umap')
pdf("figures/test_MEFeaturePlot_projected_human.pdf",height=12, width=12)
wrap_plots(plot_list, ncol=4)
dev.off()


# ME correlogram of projected data:
pdf("figures/test_ME_correlogram_projected_human.pdf",height=6, width=6)
ModuleCorrelogram(subset(NucSeq, Cell.Type == 'ASC'), sig.level = 0.001, pch.cex=2, features='hMEs')
dev.off()

```
